## UW-Madison COVID data, 2022

Plot of data from the [UW-Madison COVID
dashboard](https://covidresponse.wisc.edu/dashboard/)
after the revisions on 2022-06-06, where data is now just presented as
weekly counts. And then on 2022-06-20, they stopped providing separate
counts for students and employees, and began to just give totals.

Scraped into [`uw_covid_2022.csv`](uw_covid_2022.csv) using a
[python script](https://github.com/kbroman/UWCovid2022/blob/main/scrape_data.py)
based on the
[gist](https://gist.github.com/dgfitch/b6ca1cc61b4795e698cefdf672a90f23)
from [Dan Fitch](https://github.com/dgfitch).

We need the R package [lubridate](https://lubridate.tidyverse.org) and
the python module [requests_html](https://pypi.org/project/requests-html/).

Here, just calculating and plotting the test positivity.
The vertical line segments indicate pointwise 95% confidence intervals.
The source is in [`README.Rmd`](https://github.com/kbroman/UWCovid2021/blob/main/README.Rmd).

```{r options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE,
                      fig.path="", fig.width=11, fig.height=6)
```


```{r load_data_and_calculate}
x <- read.csv("uw_covid_2022.csv")
x <- x[x$Date != "2022-05-16",] # drop the week of 2022-05-16, because the data is bogus

x <- cbind(x, percent=x$Positive/x$Total*100)

x <- cbind(x, lo=NA, hi=NA)
for(i in 1:nrow(x)) {
    ci <- binom.test(x[i,"Positive"], x[i, "Total"])$conf.int
    x[i,"lo"] <- ci[1]*100
    x[i,"hi"] <- ci[2]*100
}
```



```{r bar_plots, dev="svg"}
light_color <- c(green="#A8DC93", blue="#B3C7E5", red="#F78FA7")[3]
dark_color <- c(green="#0D8308", blue="#0855B3", red="#C5050C")[3]

test_date <- as.Date(x[,1])

mx <- max(x[,"hi"])
par(cex=1.3)
z <- barplot(x[, "percent"], col=light_color, main="",
             las=1, ylim=c(0, mx), space=0.02,
             ylab="Percent Positive", xaxs="i")
abline(h=pretty(c(0,mx)), lty=2, col="gray60")

u <- par("usr")
v <- z[,1]
segments(v, u[3], v, u[3]-diff(u[3:4])*0.04, xpd=TRUE)
text(v, u[3] - diff(u[3:4])*0.08, x[,1], adj=c(1, 0.5), srt=45, xpd=TRUE, cex=0.8)

xx <- v
yy1 <- x[, "lo"]
yy2 <- x[, "hi"]
segments(xx, yy1, xx, yy2)

d <- 0.02 # half-width of horizontal lines at interval endpoints

segments(xx-d, yy1, xx+d, yy1)
segments(xx-d, yy2, xx+d, yy2)
```
